SCP Briefing Plots - Combined Intervention

### 2024-10-11 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
V small changes to CPR plotting script;

# data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
# data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))
# 
# nrow(data)
# 
# 
# 5463300
# 
# 4580000
# 
# 
# 359328 / 458000 * 100
# 
# 100 / 78.4559
# 
# 
# 109338 * 12.74601

>>>>

# data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
# data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))
# 
# nrow(data)
# 
# 
# 5463300
# 
# 4580000
# 
# 
# 359328 / 458000 * 100
# 
# 100 / 78.4559
# 
# 359328 * 12.74601
# 
# #2030	-1800.26	
# 
# print('RESULT 1:')
# 1800.26 * 12.74601
# 
# 
# 109338 / 1262147 * 100
# 
# 100 / 86.62906
# 
# 
# 
# 109338 * 11.5437
# 
# # 2030	-590.55		
# 
# print('RESULT 2:')
# 590.55 * 11.5437
